---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PoliticalCandidates2019

<!-- badges: start -->
![R-CMD-check](https://github.com/gchickering21/PoliticalCandidates2019/workflows/R-CMD-check/badge.svg)
<!-- badges: end -->

The goal of PoliticalCandidates2019 is to ...

## Installation

You can install the released version of PoliticalCandidates2019 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("PoliticalCandidates2019")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gchickering21/PoliticalCandidates2019")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PoliticalCandidates2019)
## basic example code
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
